---
title: "R Notebook"
output: html_notebook
---


1. Read in CSV, inspect first 10 rows.
```{r}
gdp_df = read_csv('../data/gdp_per_capita.csv')
gdp_df |> 
  head(10)
```
1(cont). Inspect last 10 rows.
```{r}
gdp_df |> 
  tail(10)
```
2. Drop the 'Value Footnotes' column, and rename the remaining columns to 'Country', 'Year', and 'GDP_Per_Capita'.
```{r}
gdp_df = gdp_df |> 
  select('Country or Area', Year, Value) |> 
  rename(Country = 'Country or Area', GDP_Per_Capita = Value)
gdp_df
```
3. Which years are represented in this dataset? 1990-2020.
How many observations are there per year? Answered in yearcount table. 

```{r}
yearcount = gdp_df |> 
  group_by(Year) |> 
  count(name = 'count')
```
```{r}
yearcount
```
3(cont). Make a plot to view the number of observations per year.

```{r}
yearcount |>
ggplot(aes(x = Year, y = count)) +
  geom_col()
```
4. How many countries are represented in this dataset? 242.
```{r}
gdp_df |> 
summarize(n_distinct(Country))
```
4(cont). Which countries have the fewest observations? Djibouti & Somalia are tied for fewest observations, with 8 each.
```{r}
gdp_df |> 
  group_by(Country) |> 
  count() |>
  arrange(n)
```
5. Create a new dataframe called 'gdp_2014' by subsetting `gdp_df` to just the year 2014.
```{r}
gdp_2014 = gdp_df |> 
  filter(Year == 2014)
```
```{r}
gdp_2014
```
6. Use summary() to find the summary statistics for GDP per capita in 2014.

```{r}
gdp_2014 |> 
 summary()
```
7. Create a histogram of GDP Per Capita numbers for 2014 (you may wish to adjust the number of bins for your histogram).

```{r}
gdp_2014 |> 
  ggplot(aes(x = GDP_Per_Capita)) +
  geom_histogram()
```







